1.5 Data Wrangling with tidyverse - R Practice

### 2019-09-10 content/r/05-r-practice.Rmd
Make practice 5 look better

## 
#### 1. Load `gapminder`. `select()` the variables `year`, `lifeExp`, `country`.

## 
#### 2. `select()` all variables *except* `pop`.

## 
#### 3. `rename()` `continent` to `cont`.

## 4. 
#### `arrange()` by year.

## 5. 
#### `arrange()` by year, but in descending order.

## 6. 
#### `arrange()` by year, then by life expectancy.

## 7. 
#### `filter()` observations with `pop` greater than 1 billion.

@@

## 9.
#### Try out the pipe (`%`) if you haven't already, by chaining commands: `select()` your data to look only at `year`, `gdpPercap`, and `country` in the year `1997`, for countries that have a `gdpPercap` greater than 20,000, and `arrange()` them alphabetically.

## 10.
#### `mutate()` a new variable called `GDP` that is equal to `gdpPercap * pop`.

## 11.
#### `mutate()` a new population variable that is the `pop` in millions.

## 12.
#### `summarize()` to get the average GDP per capita.

## 13.
#### Get the number of observations, average, minimum, maximum, and standard deviation for GDP per capita.

## 14.
#### Get the average GDP per capita over time. Hint, first `group_by()` year.

## 15.
#### Get the average GDP per capita by continent.

## 16.
#### Get the average GDP per capita by year and by continent.^[Hint: do `year` first, if you do `continent` first, there are no years to group by!] Then save this as another `tibble` called `gdp`. Create a `ggplot` of a `line` graph of average continent GDP over time using the `gdp` data.

## 17.
#### Try it again all in one command with the pipe `%>%`. Instead of saving the data as `gdp`, pipe it right into `ggplot`!^[Hint: You can use `.` as a placeholder.]

@@

## 18.

#### Import the data with `read_csv()` and assign it to `tibble` called `majors`.^[One way to avoid error messages is to move it to the same file as R's working directory, which again you can determine with `getwd()`.] The first argument of this command the name of the original file, in quotes.^[If the file is in a different folder, the argument is the full path in quotes.]

@@

## 21.
### Which major has the lowest unemployment rate?

## 22. 
#### What are the top 3 majors that have the highest percentage of women?

### 23. 
#### Make a boxplot of `Median` wage by `Major_Category`.^[You won't be able to read the labels easily, so add `theme(axis.text.x=element_text(angle=45, hjust=1)` to angle `x`-axis labels (and move them down by 1)]

### 24.
#### Which major category is the least popular in this sample?^[Hint: use `group_by` first.]

### 25. 
#### Is there a systematic difference between STEM majors and non-STEM majors? First define:

>>>>

## 1.
Load `gapminder`. `select()` the variables `year`, `lifeExp`, `country`.

## 2.
`select()` all variables *except* `pop`.

## 3.
`rename()` `continent` to `cont`.

## 4. 
`arrange()` by year.

## 5. 
`arrange()` by year, but in descending order.

## 6. 
`arrange()` by year, then by life expectancy.

## 7. 
`filter()` observations with `pop` greater than 1 billion.

@@

## 9.
Try out the pipe (`%`) if you haven't already, by chaining commands: `select()` your data to look only at `year`, `gdpPercap`, and `country` in the year `1997`, for countries that have a `gdpPercap` greater than 20,000, and `arrange()` them alphabetically.

## 10.
`mutate()` a new variable called `GDP` that is equal to `gdpPercap * pop`.

## 11.
`mutate()` a new population variable that is the `pop` in millions.

## 12.
`summarize()` to get the average GDP per capita.

## 13.
Get the number of observations, average, minimum, maximum, and standard deviation for GDP per capita.

## 14.
Get the average GDP per capita over time. Hint, first `group_by()` year.

## 15.
Get the average GDP per capita by continent.

## 16.
Get the average GDP per capita by year and by continent.^[Hint: do `year` first, if you do `continent` first, there are no years to group by!] Then save this as another `tibble` called `gdp`. Create a `ggplot` of a `line` graph of average continent GDP over time using the `gdp` data.

## 17.
Try it again all in one command with the pipe `%>%`. Instead of saving the data as `gdp`, pipe it right into `ggplot`!^[Hint: You can use `.` as a placeholder.]

@@

## 18. 
Import the data with `read_csv()` and assign it to `tibble` called `majors`.^[One way to avoid error messages is to move it to the same file as R's working directory, which again you can determine with `getwd()`.] The first argument of this command the name of the original file, in quotes.^[If the file is in a different folder, the argument is the full path in quotes.]

@@

## 21.
Which major has the lowest unemployment rate?

## 22. 
What are the top 3 majors that have the highest percentage of women?

### 23. 
Make a boxplot of `Median` wage by `Major_Category`.^[You won't be able to read the labels easily, so add `theme(axis.text.x=element_text(angle=45, hjust=1)` to angle `x`-axis labels (and move them down by 1)]

### 24.
Which major category is the least popular in this sample?^[Hint: use `group_by` first.]

### 25. 
Is there a systematic difference between STEM majors and non-STEM majors? First define:
